---
title: "Feux agricoles et pastoraux"
output:
  html_document: default

editor_options:
  chunk_output_type: console
---

# Initialization

1.  Setup layout parameters

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning = FALSE,message = FALSE)
```

2.  Setup global options

```{r Feux-agricoles-1, echo=FALSE}
# options(java.parameters = "- Xmx1024m") #Allow to increase memory limit
```

3.  Load required packages

```{r Feux-agricoles-2, message=FALSE}
library(tidyverse) # Easily Install and Load the 'Tidyverse'
library(janitor) # Simple Tools for Examining and Cleaning Dirty Data
library(readxl) # Read Excel Files
library(lubridate) # Make Dealing with Dates a Little Easier
library(annotater) # Annotate Package Load Calls, [github::luisDVA/annotater] v0.1.3
library(sf) # Simple Features for R
library(tmap) # Thematic Maps
library(leaflet) # Create Interactive Web Maps with the JavaScript 'Leaflet'
library(tmaptools) # Thematic Map Tools
library(snakecase) # Convert Strings into any Case
library(ggridges) # Ridgeline Plots in 'ggplot2'
library(pilot) # A minimal ggplot2 theme with an accessible discrete color
library(ggdist) # Visualizations of Distributions and Uncertainty
library(inspectdf) # Inspection, Comparison and Visualisation of Data Frames
library(ggforce) # Accelerating 'ggplot2'
library(report) # Automated Reporting of Results and Statistical Models
library(mapview) # Interactive Viewing of Spatial Data in R
library(caret)
```

4.  Get data

3 data origins :

-   JMO data on agriculural fires

-   JMO data on pastoral fires

-   ADMIN EXPRESS data on municipality code and location

```{r Feux-agricoles-3, echo=FALSE,message=FALSE,warning=FALSE}
agri_fire <- read_excel("data/Base feux agricoles 2001-2021-31122021.xlsx", sheet = 1)
pasto_fire <- read_excel("data/Base feux agricoles 2001-2021-31122021.xlsx", sheet = 2)
commune_gps <- read_csv2("data/commune_gps_tidied.csv")
```

# Function created

For now, I created `r length(lsf.str())` functions :

-   `r lsf.str()[1]` is a function to directly create a bubble Map

-   `r lsf.str()[2]` is a function to directly save a map to a specific folder

```{r Feux-agricoles-4, echo=FALSE}
bubble.map <- function(group_type = "agri_fire") {
  tmap_mode("view")
  fire_sf %>%
    filter(groups == group_type) %>%
    tm_shape() +
    tm_dots(
      size = "surface_ha", col = "surface_ha", palette = c("#ffffcc", "#ffeda0", "#fed976", "#feb24c", "#fd8d3c", "#fc4e2a", "#e31a1c", "#b10026"),
      title = "Burned area (ha)", alpha = 0.8, n = 8, scale = 2
    ) -> bubble_map
  print(bubble_map)
  return(bubble_map)
}

save.map <- function(map_type = "bubble", group_type = "agri_fire", directory = "local") {
  title <- "BA_"
  if (map_type == "bubble") {
    suffix <- ".html"
    title <- paste0(title, "bubble_")
    if (group_type == "agri_fire") {
      title <- paste0(title, "agri")
    } else {
      title <- paste0(title, "pasto")
    }
  } else {
    suffix <- ".png"
    tmap_mode("plot")
    title <- paste0(title, "Facet")
  }
  if (directory == "local") {
    filename <- paste0("output_data/", title)
  } else {
    filename <- paste0("M:/Departements/EF/EqFORECAST/mouillot/Feux-agricoles-pastoraux/output-data/", title)
  }
  filename <- paste0(filename, suffix)

  bubble_map <- eval(parse(text = title))
  tmap_save(bubble_map, filename)
}
```

# Data Cleaning and Tidying

1.  Data Cleaning

-> Define the class (tibble), the row (no empty month) and the column of both agricultural and pastoral data

-   Agricultural fire data

```{r Feux-agricoles-5 , echo=FALSE}
agri_fire <- as_tibble(agri_fire)
agri_fire %>%
  filter(!mois == "") %>%
  select(année:rmq) -> agri_fire

```

-   Pastoral fire data

```{r Feux-agricoles-6 , echo=FALSE}
pasto_fire <- as_tibble(pasto_fire)
pasto_fire %>%
  filter(!mois == "") %>%
  select(année:rmq) -> pasto_fire
```

2.  Data Tidying

For both data frame, :

1\. replace column names by a more rigorous way : snake case = "surface (ha)" -> "surface_ha"

2\. name columns where name has not been defined

3\. remove row with unknown mistakes (miswritten values)

4\. replace non consistent mistakes and certain values by NA

5\. Set class of each column

6\. Modify case of categorical values by snake case

7\. Create a new date column

2.  Agricultural fire data

```{r Feux-agricoles-7 , echo=FALSE}
# Rename columns
clean_names(agri_fire) -> agri_fire
agri_fire %>%
  rename(code_commune = `x4`) -> agri_fire

# Filter miswritten rows or change its value
agri_fire %>%
  filter(is.na(surface_ha)|!surface_ha==".0°4"&!surface_ha=="1,5")%>%
  mutate(surface_ha = na_if(surface_ha, "na"),
         masse_tonne_matiere_seche = na_if(masse_tonne_matiere_seche, "na"),
         type_vegetation = na_if(type_vegetation, "na"),
         lieu_de_stockage = recode(lieu_de_stockage, "na" = "not_mentioned"),
         lieu_de_stockage = na_if(lieu_de_stockage, "NA"))-> agri_fire

# Set class of each column
agri_fire %>%
  mutate(
    annee = as.integer(annee),
    mois = as.integer(mois),
    jour = as.integer(jour),
    code_commune = as.character(code_commune),
    commune = as.character(commune),
    surface_ha = as.numeric(surface_ha),
    type_vegetation = as.character(type_vegetation),
    lieu_de_stockage=as.character(lieu_de_stockage),
    masse_tonne_matiere_seche = as.numeric(masse_tonne_matiere_seche),
    source = as.factor(source),
    rmq =as.character(rmq)
  ) -> agri_fire
agri_fire %>%
  mutate(
    type_vegetation = iconv(type_vegetation, from = "UTF-8", to = "ASCII//TRANSLIT"),
    type_vegetation = to_snake_case(type_vegetation),
    type_vegetation = as.factor(type_vegetation)
  ) -> agri_fire

# Create new columns
agri_fire %>%
  mutate(
    date = make_date(annee, mois, jour),
    datemj = make_date(month = mois, day = jour)
  ) -> agri_fire
agri_fire %>%
  mutate(datemj = str_sub(datemj, -5)) -> agri_fire

# agri_fire%>%
#   filter(surface_ha=="na")%>%
#   count->na1
# test%>%
#   filter(is.na(surface_ha))%>%
#   count->na2
# na1==na2
#
# seqna1<-which(agri_fire$surface_ha=="na")
# seqna2<-which(is.na(test$surface_ha))
# tabcomp<-cbind(seqna1,seqna2)
# tabcomp<-as_tibble(tabcomp)
# tabcomp%>%
#   mutate(diff=(seqna1-seqna2))->tabcomp
# tabcomp%>%
#   filter(diff!=0)

# 370,1397,3225
```

-   Pastoral fire data

```{r Feux-agricoles-8 , echo=FALSE}
# Rename columns
clean_names(pasto_fire) -> pasto_fire

# Filter miswritten rows or change its value
pasto_fire %>%
  filter(!surface_ha=="> 100" & !surface_ha=="> 101"&!jour=="?"& !jour == "1'")%>%
  mutate(surface_ha = na_if(surface_ha, "NA"),
         surface_ha = na_if(surface_ha, "na"),
         type_vegetation = na_if(type_vegetation, "na")) -> pasto_fire

# Set class of each column
pasto_fire %>%
  mutate(
    annee = as.integer(annee),
    mois = as.integer(mois),
    jour = as.integer(jour),
    code_commune = as.character(code_commune),
    commune = as.character(commune),
    surface_ha = as.numeric(surface_ha),
    type_vegetation = as.factor(type_vegetation),
    source = as.factor(source)
  ) -> pasto_fire
pasto_fire %>%
  mutate(
    type_vegetation = iconv(type_vegetation, from = "UTF-8", to = "ASCII//TRANSLIT"),
    type_vegetation = to_snake_case(type_vegetation),
    type_vegetation = as.factor(type_vegetation)
  ) -> pasto_fire

# Create new columns
pasto_fire %>%
  mutate(
    date = make_date(annee, mois, jour),
    datemj = make_date(month = mois, day = jour)
  ) -> pasto_fire
pasto_fire %>%
  mutate(datemj = str_sub(datemj, -5)) -> pasto_fire

# pasto_fire%>%
#   filter(surface_ha=="na")%>%
#   count->na1
# test%>%
#   filter(is.na(surface_ha))%>%
#   count->na2
# na1==na2
#
# seqna1<-which(pasto_fire$surface_ha=="na")
# seqna2<-which(is.na(test$surface_ha))
# tabcomp<-cbind(seqna1,seqna2)
# tabcomp<-as_tibble(tabcomp)
# tabcomp%>%
#   mutate(diff=(seqna1-seqna2))->tabcomp
# tabcomp%>%
#   filter(diff!=0)

# 370,1397,3225
```

-   Commune GPS data

1\. change value of INSEE code of 4 digits

2\. set classe of each column

3\. separate location column into lat and long column

```{r Feux-agricoles-9 , echo=FALSE}
# Filter miswritten rows or change its value
commune_gps%>%
  mutate(code_insee=if_else(str_length(code_insee)==4, paste0(0,code_insee),code_insee))-> commune_gps

# Set class of each column
commune_gps %>%
  mutate(code_insee = as.character(code_insee)) -> commune_gps

# Create new columns
commune_gps %>%
  separate(geo_point_2d, c("lat", "lon"), sep = ",") %>%
  mutate(
    lon = as.numeric(lon),
    lat = as.numeric(lat)
  ) -> commune_gps
```

3.  Data merging

-> Merge agricultural and pastoral data

-> Add data of municipality

```{r Feux-agricoles-10 ,echo=FALSE}
fire_mix <- bind_rows("agri_fire" = agri_fire, "pasto_fire" = pasto_fire, .id = "groups")
fire <- left_join(fire_mix, commune_gps, by = c("code_commune" = "code_insee"))
fire %>%
  filter(!is.na(lat)) -> fire
fire%>%
  mutate(groups=if_else(!is.na(lieu_de_stockage),"build_agri_fire",groups))->fire
# fire%>%
# filter(is.na(lat))%>%
#   count(code_commune)->unavailable_loc
```

4.  Creating other format files

-> Create a sf file of the database

```{r Feux-agricoles-11, echo=FALSE}
fire_sf <- st_as_sf(fire,
  coords = c("lon", "lat"),
  crs = "+proj=longlat +datum=WGS84 +nodefs"
)
```

# Data prediction

```{r}
fire%>%
  filter(!is.na(surface_ha),
         !is.na(type_vegetation))%>%
  select(surface_ha,annee,mois,lat,lon)->fire_for_training

fire%>%
  filter(is.na(surface_ha),
         !is.na(type_vegetation))%>%
  select(surface_ha,annee,mois,lat,lon)->fire_for_prediction



model <- train(surface_ha ~ mois,
               data = fire_for_training,
               method = "lm")
fitControl <- trainControl(method = "repeatedcv",   
                           number = 10,     # number of folds
                           repeats = 10,
                           search = "random")    # repeated ten times

model.cv <- train(surface_ha ~ .,
               data = fire_for_training,
               method = "ridge",  # now we're using the lasso method
               trControl = fitControl,
               preProcess = c('scale', 'center'))  

model.cv   
pred<-predict(model.cv,fire_for_prediction)
```

# Data exploration

## 1. Graphic exploration

### 1. Global overview

```{r ,echo=FALSE,message=FALSE}
fire%>%
  select(!date)%>%
  mutate(type_vegetation=as.character(type_vegetation),
         source=as.character(source))%>%
  report(distribution=FALSE)%>%
  summary()->Data_report
print(Data_report)
```

```{r,echo=FALSE}
fire%>%
  inspect_na()%>%
  show_plot()+
  theme_pilot()->NA_Variable_barplot
print(NA_Variable_barplot)
```

```{r,echo=FALSE}
fire%>%
  inspect_num()%>%
  show_plot(plot_layout = c(2,4))+
  theme_pilot()->Variable_histogram
print(Variable_histogram)

```

```{r,echo=FALSE}
fire_for_training%>%
  select(!names(fire)[str_detect(names(fire),pattern = "commune")]&
         !date&
         !datemj)%>%
  inspect_cat()%>%
  show_plot()+
  theme_pilot()+
  theme(legend.position="none")->Variable_Frequency_barplot
print(Variable_Frequency_barplot)
```

### 2. Temporal exploration

```{r,echo=FALSE,message=FALSE}
fire %>%
  ggplot() +
  aes(x = date, color = groups, fill = groups) +
  geom_density(alpha = 0.5, adjust = 1 / 10) +
  labs(color = "Type of fire event",
       fill = "Type of fire event",
       x = "Year",
       y = "Density of fire events"
      ) +
  theme_pilot() +
  scale_color_pilot(labels = c("Cropland fire","Agricultural building fire","Rangeland fire"))+
  scale_fill_pilot(labels = c("Cropland fire","Agricultural building fire","Rangeland fire"))-> NbFire_Date_density
print(NbFire_Date_density)
```

```{r,echo=FALSE}
fire %>%
  group_by(groups, annee, mois) %>%
  count() %>%
  group_by(groups, mois) %>%
  summarise(mean = mean(n)) %>%
  ggplot() +
  aes(x = as.factor(mois), fill = groups, color = groups, y = mean) +
  geom_bar(stat = "identity") +
  labs(color = "Type of fire event", 
       fill = "Type of fire event",
       x = "Month",
       y = "Mean number of fire event per year") +
    theme_pilot() +
  scale_color_pilot(labels =  c("Cropland fire","Agricultural building fire","Rangeland fire"))+
  scale_fill_pilot(labels =  c("Cropland fire","Agricultural building fire","Rangeland fire"))-> MeanNbFire_Month_barplot 
print(MeanNbFire_Month_barplot)

```

```{r,echo=FALSE}
fire %>%
  filter(annee!=c(2000,2001))%>%
  ggplot() +
  aes(x = datemj, y = groups, group = groups, color = groups, fill = groups) +
  geom_density_ridges2() +
  xlab("Date") +
  ylab("Number of fire events") +
  labs(color = "Type of fire event", fill = "Type of fire event") +
  theme_pilot() +
  scale_color_pilot(labels = c("Agricultural fire", "Pastoral fire"))+
  scale_fill_pilot(labels = c("Agricultural fire", "Pastoral fire")) +
  facet_wrap(~annee, ncol = 1, strip.position = "right") +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank(),
    axis.text.y = element_blank(),
    panel.spacing = unit(0, "lines"),
    axis.text.x=element_blank()
  ) -> NbFire.Year_JJMM_density
print(NbFire.Year_JJMM_density)
```

### 3. Spatial exploration

```{r,echo=FALSE}
fire %>%
  mutate(code_commune_lump = fct_lump(code_commune, prop = .0009)) %>%
  filter(code_commune_lump != "Other") %>%
  ggplot() +
  aes(x = fct_infreq(commune.y), color = groups, fill = groups) +
  geom_bar() +
  coord_flip() +
  xlab("Municipality") +
  ylab("Count") +
  ggtitle("Most affected municipalities over the study period, (corresponding to 0.09% of data)") +
  labs(color = "Type of fire event", fill = "Type of fire event",
       x="Number of fire events") +
  theme_pilot() +
  scale_color_pilot(labels = c("Agricultural fire", "Pastoral fire"))+
  scale_fill_pilot(labels = c("Agricultural fire", "Pastoral fire")) -> City_Nb_barplot
print(City_Nb_barplot)
```

```{r,echo=FALSE}
fire%>%
   mutate(departement_lump = fct_lump(departement, prop = .005, ))%>%
  ggplot() +
  aes(x = fct_infreq(departement_lump), fill= groups) +
  geom_bar() +
  coord_flip() +
  xlab("Departements") +
  ylab("Count") +
  ggtitle("Count of fire in each french departement") +
  theme(axis.text.y = element_text(size=10))+
  theme_pilot() +
  scale_color_pilot()+
  scale_fill_pilot()-> Departement_Count_Barplot
print(Departement_Count_Barplot)
```

```{r,echo=FALSE}
tmap_mode("view")
bubble.map("agri_fire") -> BA_bubble_agri
```

```{r, echo=FALSE}
tmap_mode("view")
bubble.map("pasto_fire") -> BA_bubble_pasto
```

```{r, echo=FALSE}
# fire%>%
#   ggplot()+
#   aes(x=lon,y=lat)+
#   geom_density_2d_filled()+
#   facet_wrap(~groups)+
#     xlab("Vegetation type")+
#   ylab("Burned Area (ha)")+
#   ggtitle("Burned Area of most common vegetation type, include only fires<50 ha")+
#   theme_bw()
# fire_sf_density<-density(x = fire_sf$code_commune)
# tm_shape(fire_sf)
```

```{r, echo=FALSE}
tmap_mode("plot")
osm_fire_sf <- read_osm(fire_sf, ext = 1.1)
tm_shape(osm_fire_sf) +
  tm_rgb() +
  tm_shape(fire_sf) +
  tm_tiles("OpenStreetMap") +
  tm_dots(
    col = "groups",
    title = "Burned area (ha)",
    palette = pilot_color()[c(1,length(pilot_color()))],
    alpha = 0.8,
    n = 8,
    scale = 2,
    legend.show = F
  ) +
  tm_facets(by = "groups", free.coords = F) +
  tm_layout(panel.labels = c("Agricultural fire events", "Pastoral fire events")) -> BA_Facet
print(BA_Facet)
```

```{r}
fire_sf%>%
  ggplot()+
  aes(color=groups)+
  geom_sf(alpha=0.6)+
  theme_minimal()+
  scale_color_pilot(labels = c("Cropland fire","Agricultural building fire","Rangeland fire"))+
  scale_size_area(max_size = 25)+
    labs(color = "Type of fire event",
       size = "Burned area (ha)"
        
      )+
  borders("france")-> Group_bubblemap
print(Group_bubblemap)
```

```{r, echo=FALSE}
fire_sf%>%
  ggplot()+
  aes(color=groups,size=surface_ha)+
  geom_sf(alpha=0.6)+
  theme_minimal()+
  scale_color_pilot(labels = c("Cropland fire","Agricultural building fire","Rangeland fire"))+
  scale_size_area(max_size = 25)+
    labs(color = "Type of fire event",
       size = "Burned area (ha)"
        
      )+
  borders("france")-> BA_Group_bubblemap
print(BA_Group_bubblemap)
```

```{r, echo=FALSE}
fire_sf%>%
  ggplot()+
  aes(color=groups,size=masse_tonne_matiere_seche)+
  geom_sf(alpha=0.6)+
  theme_minimal()+
  scale_color_pilot(labels = c("Cropland fire","Agricultural building fire","Rangeland fire"))+
  scale_size_area(max_size = 25)+
    labs(color = "Type of fire event",
       size = "Mass of dry matter (ton)"
        
      )+
  borders("france")-> MassDry_Group_bubblemap
print(MassDry_Group_bubblemap)
```

```{r,echo=FALSE}
mapview(fire_sf, zcol="groups")
```

```{r,echo=FALSE}
mapview(fire_sf, cex="surface_ha")
```

### 4. Focus on Vegetation type

```{r,echo=FALSE}
fire %>%
  mutate(type_vegetation_lump = fct_lump(type_vegetation, prop = .004, )) %>%
  ggplot() +
  aes(x = fct_infreq(type_vegetation_lump), color = groups, fill = groups) +
  geom_bar() +
  coord_flip() +
  xlab("Vegetation type") +
  ylab("Count") +
  ggtitle("Frequence of each vegetation type") +
  labs(color = "Type of fire event", fill = "Type of fire event") +
  theme_pilot() +
  scale_color_pilot(labels = c("Agricultural fire", "Pastoral fire"))+
  scale_fill_pilot(labels = c("Agricultural fire", "Pastoral fire")) -> VegetType_Nb_barplot
print(VegetType_Nb_barplot)
```

```{r,echo=FALSE}
level_of_fire <- as.tibble(levels(as.factor(fire$type_vegetation)))
# level_of_fire%>%
# filter(str_detect(value, "chaume") & str_detect(value, "ble"))
word_in_fire <- str_extract_all(level_of_fire, "[a-z]+")
as.tibble(word_in_fire[[1]]) %>%
  mutate(value_lump = fct_lump(value, prop = .003, )) %>%
  ggplot() +
  aes(x = fct_infreq(value_lump)) +
  geom_bar() +
  coord_flip() +
  xlab("Word inside vegetation type") +
  ylab("Count") +
  ggtitle("Frequence of each word among the 402 vegetation type, nb words = 818") +
  theme_pilot() +
  scale_color_pilot()+
  scale_fill_pilot() -> Words_Nb_barplot
print(Words_Nb_barplot)
```

```{r,echo=FALSE}
fire %>%
  mutate(type_vegetation_lump = fct_lump(type_vegetation, prop = .004, )) %>%
  filter(type_vegetation_lump != "Other" & surface_ha < 50) %>%
  ggplot() +
  aes(x = type_vegetation_lump, y = surface_ha) +
  stat_halfeye() +
  coord_flip() +
  xlab("Vegetation type") +
  ylab("Burned Area (ha)") +
  ggtitle("Burned Area of most common vegetation type, include only fires<50 ha") +
  theme_pilot() +
  scale_color_pilot()+
  scale_fill_pilot() -> VegetType_Surface_distplot
print(VegetType_Surface_distplot)
```

### 5. Focus on Burned Area

```{r}
fire%>%
  mutate(groups=as.numeric(as.factor(groups)))%>%
  ggplot()+
  aes(x =groups,
      y=surface_ha,
      color = groups) +
    geom_jitter(alpha = 0.5,
                width=.2) +
    labs(title = "Distribution of Burned area ~ type of fire",
         subtitle = "Dark blue = Agricultural fire, Light blue = Pastoral fire",
         x = "Fire type",
         y = "Burned area (ha)") +
  theme(legend.position = "none",
        axis.text.x = element_blank())+
  facet_zoom(ylim = c(0, 200), xlim= c(0.8,2.2),zoom.size = 0.5)-> BA_Group_jitterplot
print(BA_Group_jitterplot)
```

# Export data

1.  Export data

```{r Feux-agricoles-14 ,echo=FALSE}
write_csv2(fire,"Agricultural-Pastoral_Fire.csv")
```

2.  Export figures

```{r Feux-agricoles-15 ,echo=FALSE}
ggsave(NA_Variable_barplot, filename = "NA_Variable_barplot.png", path = "M:/Departements/EF/EqFORECAST/mouillot/Feux-agricoles-pastoraux/output-data/")
ggsave(NA_Variable_barplot, filename = "NA_Variable_barplot.png", path = "output_data")
ggsave(Variable_histogram, filename = "Variable_histogram.png", path = "M:/Departements/EF/EqFORECAST/mouillot/Feux-agricoles-pastoraux/output-data/")
ggsave(Variable_histogram, filename = "Variable_histogram.png", path = "output_data")
ggsave(Variable_Frequency_barplot, filename = "Variable_Frequency_barplot.png", path = "M:/Departements/EF/EqFORECAST/mouillot/Feux-agricoles-pastoraux/output-data/")
ggsave(Variable_Frequency_barplot, filename = "Variable_Frequency_barplot.png", path = "output_data")
ggsave(NbFire_Date_density, filename = "NbFire_Date_density.png", path = "M:/Departements/EF/EqFORECAST/mouillot/Feux-agricoles-pastoraux/output-data/")
ggsave(NbFire_Date_density, filename = "NbFire_Date_density.png", path = "output_data")
ggsave(MeanNbFire_Month_barplot, filename = "MeanNbFire_Month_barplot.png", path = "M:/Departements/EF/EqFORECAST/mouillot/Feux-agricoles-pastoraux/output-data/")
ggsave(MeanNbFire_Month_barplot, filename = "MeanNbFire_Month_barplot.png", path = "output_data")
ggsave(VegetType_Nb_barplot, filename = "VegetType_Nb_barplot.png", path = "M:/Departements/EF/EqFORECAST/mouillot/Feux-agricoles-pastoraux/output-data/")
ggsave(VegetType_Nb_barplot, filename = "VegetType_Nb_barplot.png", path = "output_data")
ggsave(City_Nb_barplot, filename = "City_Nb_barplot.png", path = "M:/Departements/EF/EqFORECAST/mouillot/Feux-agricoles-pastoraux/output-data/")
ggsave(City_Nb_barplot, filename = "City_Nb_barplot.png", path = "output_data")
ggsave(Words_Nb_barplot, filename = "Words_Nb_barplot.png", path = "M:/Departements/EF/EqFORECAST/mouillot/Feux-agricoles-pastoraux/output-data/")
ggsave(Words_Nb_barplot, filename = "Words_Nb_barplot.png", path = "output_data")
ggsave(VegetType_Surface_distplot, filename = "VegetType_Surface_distplot.png", path = "M:/Departements/EF/EqFORECAST/mouillot/Feux-agricoles-pastoraux/output-data/")
ggsave(VegetType_Surface_distplot, filename = "VegetType_Surface_distplot.png", path = "output_data")
ggsave(NbFire.Year_JJMM_density, filename = "NbFire.Year_JJMM_density.png", path = "M:/Departements/EF/EqFORECAST/mouillot/Feux-agricoles-pastoraux/output-data/")
ggsave(NbFire.Year_JJMM_density, filename = "NbFire.Year_JJMM_density.png", path = "output_data")
ggsave(Departement_Count_Barplot, filename = "Departement_Count_Barplot.png", path = "M:/Departements/EF/EqFORECAST/mouillot/Feux-agricoles-pastoraux/output-data/")
ggsave(Departement_Count_Barplot, filename = "Departement_Count_Barplot.png", path = "output_data")
tmap_mode("view")
for (group_type in c("agri_fire", "pasto_fire")) {
  for (directory in c("local", "mouillot")) {
    save.map(map_type = "bubble", group_type = group_type, directory = directory)
  }
}
tmap_mode("plot")
for (directory in c("local", "mouillot")) {
  save.map(map_type = "BA", directory = directory)
}
```
