---
title: "01_Data_cleaning_and_tidying"
output:
  html_document: default
editor_options:
  chunk_output_type: console
---

# Initialization

## 1. Setup layout parameters

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

## 2. Setup global options

```{r Feux-agricoles-1, echo=FALSE}
# options(java.parameters = "- Xmx1024m") #Allow to increase memory limit
```

## 3. Load required packages

```{r Feux-agricoles-2, message=FALSE}
library(raster)
library(tidyverse) # Easily Install and Load the 'Tidyverse'
library(janitor) # Simple Tools for Examining and Cleaning Dirty Data
library(readxl) # Read Excel Files
library(lubridate) # Make Dealing with Dates a Little Easier
library(annotater) # Annotate Package Load Calls, [github::luisDVA/annotater] v0.1.3
library(sf) # Simple Features for R
library(tmap) # Thematic Maps
library(leaflet) # Create Interactive Web Maps with the JavaScript 'Leaflet'
library(tmaptools) # Thematic Map Tools
library(snakecase) # Convert Strings into any Case
library(ggridges) # Ridgeline Plots in 'ggplot2'
library(pilot) # A minimal ggplot2 theme with an accessible discrete color
library(ggdist) # Visualizations of Distributions and Uncertainty
library(inspectdf) # Inspection, Comparison and Visualisation of Data Frames
library(ggforce) # Accelerating 'ggplot2'
library(report) # Automated Reporting of Results and Statistical Models
library(mapview) # Interactive Viewing of Spatial Data in R
library(caret)
library(foreach)
library(doParallel)
```

## 4. Get data

3 data origins :

-   JMO data on agriculural fires

-   JMO data on pastoral fires

-   ADMIN EXPRESS data on municipality code and location

```{r Feux-agricoles-3, echo=FALSE,message=FALSE,warning=FALSE}
agri_fire <- read_excel("data/Base feux agricoles 2001-2021-31122021.xlsx", sheet = 1)
pasto_fire <- read_excel("data/Base feux agricoles 2001-2021-31122021.xlsx", sheet = 2)
commune_gps <- read_csv2("data/commune_gps_tidied.csv")
```

# Data Cleaning and Tidying

## 1. Data Cleaning

-> Define the class (tibble), the row (no empty month) and the column of both agricultural and pastoral data

-   Agricultural fire data

```{r Feux-agricoles-5 , echo=FALSE}
agri_fire <- as_tibble(agri_fire)
agri_fire %>%
  filter(!mois == "") %>%
  dplyr::select(année:rmq) -> agri_fire
```

-   Pastoral fire data

```{r Feux-agricoles-6 , echo=FALSE}
pasto_fire <- as_tibble(pasto_fire)
pasto_fire %>%
  filter(!mois == "") %>%
  dplyr::select(année:rmq) -> pasto_fire
```

## 2. Data Tidying

For both data frame, :

1\. replace column names by a more rigorous way : snake case = "surface (ha)" -> "surface_ha"

2\. name columns where name has not been defined

3\. remove row with unknown mistakes (miswritten values)

4\. replace non consistent mistakes and certain values by NA

5\. Set class of each column

6\. Modify case of categorical values by snake case

7\. Create a new date column

### - Agricultural fire data

```{r Feux-agricoles-7 , echo=FALSE}
# Rename columns
clean_names(agri_fire) -> agri_fire
agri_fire %>%
  rename(code_commune = `x4`) -> agri_fire

# Filter miswritten rows or change its value
agri_fire %>%
  filter(is.na(surface_ha) | !surface_ha == ".0°4" & !surface_ha == "1,5") %>%
  mutate(
    surface_ha = na_if(surface_ha, "na"),
    masse_tonne_matiere_seche = na_if(masse_tonne_matiere_seche, "na"),
    type_vegetation = na_if(type_vegetation, "na"),
    lieu_de_stockage = recode(lieu_de_stockage, "na" = "not_mentioned"),
    lieu_de_stockage = na_if(lieu_de_stockage, "NA")
  ) -> agri_fire

# Set class of each column
agri_fire %>%
  mutate(
    annee = as.integer(annee),
    mois = as.integer(mois),
    jour = as.integer(jour),
    code_commune = as.character(code_commune),
    commune = as.character(commune),
    surface_ha = as.numeric(surface_ha),
    type_vegetation = as.character(type_vegetation),
    lieu_de_stockage = as.character(lieu_de_stockage),
    masse_tonne_matiere_seche = as.numeric(masse_tonne_matiere_seche),
    source = as.factor(source),
    rmq = as.character(rmq)
  ) -> agri_fire
agri_fire %>%
  mutate(
    type_vegetation = iconv(type_vegetation, from = "UTF-8", to = "ASCII//TRANSLIT"),
    type_vegetation = to_snake_case(type_vegetation),
    type_vegetation = as.factor(type_vegetation)
  ) -> agri_fire

# Create new columns
agri_fire %>%
  mutate(
    date = make_date(annee, mois, jour),
    datemj = str_sub(date, -5),
    dateym = str_sub(date, end = 7)
  ) -> agri_fire

# agri_fire%>%
#   filter(surface_ha=="na")%>%
#   count->na1
# test%>%
#   filter(is.na(surface_ha))%>%
#   count->na2
# na1==na2
#
# seqna1<-which(agri_fire$surface_ha=="na")
# seqna2<-which(is.na(test$surface_ha))
# tabcomp<-cbind(seqna1,seqna2)
# tabcomp<-as_tibble(tabcomp)
# tabcomp%>%
#   mutate(diff=(seqna1-seqna2))->tabcomp
# tabcomp%>%
#   filter(diff!=0)

# 370,1397,3225
```

### - Pastoral fire data

```{r Feux-agricoles-8 , echo=FALSE}
# Rename columns
clean_names(pasto_fire) -> pasto_fire

# Filter miswritten rows or change its value
pasto_fire %>%
  filter(!surface_ha == "> 100" & !surface_ha == "> 101" & !jour == "?" & !jour == "1'") %>%
  mutate(
    surface_ha = na_if(surface_ha, "NA"),
    surface_ha = na_if(surface_ha, "na"),
    type_vegetation = na_if(type_vegetation, "na")
  ) -> pasto_fire

# Set class of each column
pasto_fire %>%
  mutate(
    annee = as.integer(annee),
    mois = as.integer(mois),
    jour = as.integer(jour),
    code_commune = as.character(code_commune),
    commune = as.character(commune),
    surface_ha = as.numeric(surface_ha),
    type_vegetation = as.factor(type_vegetation),
    source = as.factor(source)
  ) -> pasto_fire
pasto_fire %>%
  mutate(
    type_vegetation = iconv(type_vegetation, from = "UTF-8", to = "ASCII//TRANSLIT"),
    type_vegetation = to_snake_case(type_vegetation),
    type_vegetation = as.factor(type_vegetation)
  ) -> pasto_fire

# Create new columns
pasto_fire %>%
  mutate(
    date = make_date(annee, mois, jour),
    datemj = str_sub(date, -5),
    dateym = str_sub(date, end = 7)
  ) -> pasto_fire

# pasto_fire%>%
#   filter(surface_ha=="na")%>%
#   count->na1
# test%>%
#   filter(is.na(surface_ha))%>%
#   count->na2
# na1==na2
#
# seqna1<-which(pasto_fire$surface_ha=="na")
# seqna2<-which(is.na(test$surface_ha))
# tabcomp<-cbind(seqna1,seqna2)
# tabcomp<-as_tibble(tabcomp)
# tabcomp%>%
#   mutate(diff=(seqna1-seqna2))->tabcomp
# tabcomp%>%
#   filter(diff!=0)

# 370,1397,3225
```

### - Commune GPS data

1\. change value of INSEE code of 4 digits

2\. set classe of each column

3\. separate location column into lat and long column

```{r Feux-agricoles-9 , echo=FALSE}
# Filter miswritten rows or change its value
commune_gps %>%
  mutate(code_insee = if_else(str_length(code_insee) == 4, paste0(0, code_insee), code_insee)) -> commune_gps

# Set class of each column
commune_gps %>%
  mutate(code_insee = as.character(code_insee)) -> commune_gps

# Create lon/lat columns
commune_gps %>%
  separate(geo_point_2d, c("lat", "lon"), sep = ",") %>%
  mutate(
    lon = as.numeric(lon),
    lat = as.numeric(lat)
  ) -> commune_gps

# Create code_departement column
commune_gps %>%
  mutate(code_departement = str_sub(code_insee, end = -4)) -> commune_gps
```

## 3. Data merging

-> Merge agricultural and pastoral data

-> Add data of municipality

```{r Feux-agricoles-10 ,echo=FALSE}
fire_mix <- bind_rows("agri_fire" = agri_fire, "pasto_fire" = pasto_fire, .id = "groups")
fire <- left_join(fire_mix, commune_gps, by = c("code_commune" = "code_insee"))
fire %>%
  filter(!is.na(lat)) -> fire
fire %>%
  mutate(groups = if_else(!is.na(lieu_de_stockage), "build_agri_fire", groups)) -> fire
# fire%>%
# filter(is.na(lat))%>%
#   count(code_commune)->unavailable_loc
```

## 4. Creating other format files

-> Create a sf file of the database

```{r Feux-agricoles-11, echo=FALSE}
fire_sf <- st_as_sf(fire,
  coords = c("lon", "lat"),
  crs = "+proj=longlat +datum=WGS84 +nodefs"
)
```

# Export data

```{r Feux-agricoles-14 ,echo=FALSE}
write_csv2(fire, "data/Working_files/Agricultural_Pastoral_Fire_01.csv")
st_write(fire_sf, "data/Working_files/Agricultural_Pastoral_Fire_sf_01.gpkg", append = FALSE)
write_csv2(fire, "data/Working_files/Agricultural_Pastoral_Fire.csv")
st_write(fire_sf, "data/Working_files/Agricultural_Pastoral_Fire_sf.gpkg", append = FALSE)
```